\chapter*{\Large Acknowledgments}

I would like to thank Dr.\ Luca Cortese, Dr.\ O. Ivy Wong and Dr.\ Barbara Catinella for their extraordinary support in my master's research.
When I started this research in Australia in August 2018, every single step was new and really hard to me.
I did not know many things about basic galaxy properties, radio astronomy and even how to make a progress in the research.
However, every time I faced a problem, they spared the time and gave me a help and an advice.
I am really grateful for their kindness and I think it is impossible for my research project to reach the level.
I am also thank to all of my frinds I met in International Centre for Radio Astronomy Research (ICRAR), Australia.
They were always kind to me and gave me much help when I had a problem to use ds9, python or other applications.
During my staying there in a total of about five months, I discussed various fields of astrophysics and also politics, economics and future in the world with them.
This experience broaden my horizons and makes my two years master's course much more fruitful.

I would like to thank Dr.\ Tsutomu T. Takeuchi, my supervisor in Nagoya university.
He gave me so many opportunities to go outside university and to get a wide knowledge not only in astronomy.
He was really thoughtful and gave me shrewd advice every time I got stuck on a problem.
His admired knowledge in astrophysics, statistics, linguistics, etc. expands my perspective to "study".
I am really grateful for everything he has done for me.

I would like to thank my colleagues and friends in Nagoya university.
They always supported me when I was suffering the research and my life.

I would like to thank my parents to raise me until now and spend so much money and time.

This project would have been impossible without the funding from Nagoya University (Overseas Challenge Program for Young Researchers 2019).
