\section*{Thesis Declaration}
\vskip 0.8cm
\begin{flushleft}
I, insert name, certify that: [DELETE ALL IRRELEVANT STATEMENTS]
\vskip 0.5cm 
This thesis has been substantially accomplished during enrolment in the degree.
\vskip 0.25cm
This thesis does not contain material which has been accepted for the award of any other degree or diploma in my name, in any university or other tertiary institution.
\vskip 0.25cm
No part of this work will, in the future, be used in a submission in my name, for any other degree or diploma in any university or other tertiary institution without the prior approval of The University of Western Australia and where applicable, any partner institution responsible for the joint-award of this degree.
\vskip 0.25cm
This thesis does not contain any material previously published or written by another person, except where due reference has been made in the text. 
\vskip 0.25cm
The work(s) are not in any way a violation or infringement of any copyright, trademark, patent, or other rights whatsoever of any person.
\vskip 0.25cm
The research involving human data reported in this thesis was assessed and approved by The University of Western Australia Human Research Ethics Committee. Approval \#: [insert approval number(s)].
\vskip 0.25cm
Written patient consent has been received and archived for the research involving patient data reported in this thesis.
\vskip 0.25cm
The research involving animal data reported in this thesis was assessed and approved by The University of Western Australia Animal Ethics Committee. Approval \#: [insert approval number(s)].
\vskip 0.25cm
The research involving animals reported in this thesis followed The University of Western Australia and national standards for the care and use of laboratory animals.
\vskip 0.25cm
The following approvals were obtained prior to commencing the relevant work described in this thesis: [List approvals here].
\vskip 0.25cm
Third party editorial assistance was provided in preparation of the thesis by [insert name/company].
\vskip 0.25cm
The work described in this thesis was funded by [insert name of grant and grant identification numbers].
\vskip 0.25cm
Technical assistance was kindly provided by [insert name of assistant(s)] for [insert description of assistance] that is described in [insert location in thesis].
\vskip 0.25cm
This thesis contains published work and/or work prepared for publication, some of which has been co-authored. 
\vskip 0.5cm
Signature: [Sign here]
\vskip 0.25cm
Date: [Insert date here]
\end{flushleft}